Big Tech is censoring me: \\ Using social media data to verify the platforms' regulation policies regarding ``misinformation''

### 2021-07-07 article/draft.tex
updates

\title{Very Preliminary Draft}

@@

Using social media data to verify the platforms' regulation policies regarding ``misinformation''

@@

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

@@

First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}. This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  ``YouTube suspends OANN for violating its Covid-19 policy''. nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021. For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban. We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$. The number of articles published per day was around $50$ until December $20$, $2019$. The this number decreased drastically to reach a {\color{pink} plateau} around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel). The communication around the ban may have discouraged The Beauty of Life to proceed with their activity. Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained. It started on December $1$, $2019$, and was still enforced in June 2021.

\subsection{Reducing the visibility}

@@

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID19 or presidential elections) and  redirect users to a URL link to get more context. Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts. At the account level, notices can indicate whether an account has been temporarily or permanently suspended.

@@

Finally, to the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
	%\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_1.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_3.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/youtube_panels/yt_4.png} 
	%\end{multicols}
	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
	\label{fig9}
\end{figure}

@@

We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}. We recorded the number of videos containing an information panel within each category. For COVID19 and vaccine related videos more than half of the videos contained an information panel. {\color{pink} Nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.} In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either. Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.

@@

For climate change we only examined $18$ misleading videos and we found that $72\%$ did not display an information panel. Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos. Therefore, it is likely that Youtube add information panels below videos conecrning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.

\begin{table}[] 
\begin{tabular}{|c|c|c|c|c|}
\hline
Category       & \begin{tabular}[c]{@{}c@{}}With \\ information \\ panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Without  \\\ information \\ panel\end{tabular} & Total & \begin{tabular}[c]{@{}c@{}}IP \% \end{tabular} \\ \hline
\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & 0                                                                 & 11                                                                   & 11    & 0                                                       \\ \hline
Vaccine        & 21                                                                & 7                                                                    & 28    & 75                                                      \\ \hline
COVID19          & 73                                                                & 43                                                                   & 116   & 63                                                      \\ \hline
\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & 5                                                                 & 13                                                                   & 18    & 28                                                      \\ \hline
\end{tabular}
\caption{}
\label{tab2}
\end{table}

@@

\begin{table*}[h]
\begin{tabular}{|c|c|c|}
\hline
\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Policy regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline

\end{tabular}
\caption{Summary of ressources, last accessed on July 5, 2021. }
\label{summary}
\end{table*}

>>>>

\title{Big Tech is censoring me: \\ Using social media data to verify the platforms' regulation policies regarding ``misinformation''}

@@

'Big Tech is censoring me': Using social media data to verify the platforms' regulation policies regarding ``misinformation''

@@

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

@@

First, we investigate the temporary suspension case of the Youtube Channel of {\it One America News channel}. This channel received a first strike on November 24, 2020 for the promotion of  a false cure for COVID19.\footnote{See nbcnews,  \href{https://www.nbcnews.com/news/all/youtube-suspends-oann-violating-its-covid-19-policy-n1248845}{YouTube suspends OANN for violating its Covid-19 policy} nbcnews, Ahiza García-Hodges, 24 11 2020.} We collected the activity of the channel OANN (video counts, view counts) using  the Youtube API v3, between November 2020 and January 2021. For the video counts, we used the playlist endpoint to retrieve the videos uploaded with their publishing date and for the view count we used the IDs of the videos we had from the playlists and via the videos endpoint we retrieved the view counts on June 2021.\footnote{See the Google documentation  \href{https://developers.google.com/youtube/v3/docs/videos/list}{https://developers.google.com/youtube/v3/docs/videos/list} and \href{https://developers.google.com/youtube/v3/docs/playlists/list}{https://developers.google.com/youtube/v3/docs/playlists/list}}

@@

The number of Facebook reactions, shares and comments dropped to zero for TheBL’s articles published after December $1$, $2019$ (see figure \ref{fb_bl} top panel), indicating the start of the ban. We can note that although the ban was communicated in an article published\footnote{See \href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us}.} on December $20$, $2019$, it seems to have actually started on December $1$, $2019$. The number of articles published per day was around $50$ until December $20$, $2019$. This number decreased drastically to reach around $5$ to $10$ articles published per day (see figure \ref{fb_bl} bottom panel). The communication around the ban may have discouraged The Beauty of Life to proceed with their activity. Using Buzzsumo data, a global ban over sharing a thebl.com URL link on Facebook was ascertained. It started on December $1$, $2019$, and was still enforced in June 2021.

\href{https://help.twitter.com/en/safety-and-security/phishing-spam-and-malware-links}{link}
\subsection{Reducing the visibility}

@@

Alongside other social networking platforms, when the content of a tweet violates the Twitter rules, a notice can be added to provide more context according to Twitter's Help Center.\footnote{See Notices on Twitter and what they mean: \href{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}{https://help.twitter.com/en/rules-and-policies/notices-on-twitter}.} At the tweet level, notices take the form of a label or an interstitial. Labels are context specific (e.g. COVID19 or presidential elections) and  redirect users to a URL link to get more context (see figure \ref{fig8} for an example). Interstitials are presented as a greyed box on top of a tweet, which indicate sensitive content, violations of Twitter rules, withheld tweets for violation of local laws or even tweets from suspended accounts (see figure \ref{fig_notice} for an example). At the account level, notices can indicate whether an account has been temporarily or permanently suspended.

{\color{red} To the best of our knowledge, when using the Twitter API v2, there is no field which indicates whether a tweet is labeled or not; while the interstitial ``possibly sensitive'' and ``withheld" are both Tweet fields that can be recovered\footnote{See \href{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}{https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet}.} from the API.  ............... so say minet tw scrape, scraper was enriched to get information about labels!}

@@

The Twitter Safety announced in a Tweet that 
%https://twitter.com/TwitterSafety/status/1379515615954620418

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png}
	%\end{multicols}
	\caption{Panel (a): Tweet containing a URL link hidden behind an interstitial. Panel (b): when clicking on $view$, to view the content hidden behind the interstitial. Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

\begin{figure}
	\centering
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_1.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_2.png} 
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_3.png}
	%\end{multicols}
	%\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/youtube_panels/yt_4.png} 
	%\end{multicols}
	\caption{Top to buttom respectively: information panel displayed under some videos related to climate change, COVID19 vaccine, COVID19 and elections.}
	\label{fig9}
\end{figure}

@@

We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}. We recorded the number of videos containing an information panel within each category. For COVID19 and vaccine related videos more than half of the videos contained an information panel. Nevertheless, we noticed that duplicates of the same Youtube video can get uploaded under different video titles and that the information panel appears under the some duplicates, but not for all. In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either. Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.

@@

For climate change we only examined $18$ misleading videos and we found that $28\%$ did not display an information panel. Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos. Therefore, it is likely that Youtube add information panels below videos concerning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine. 
%drop last colum
%add % in a second line
\begin{table}[] 
\begin{tabular}{|c|c|c|c|c|}
\hline
Category       & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos with \\ an information panel\end{tabular} & \begin{tabular}[c]{@{}c@{}}Number of Youtube \\ videos without \\ an information panel\end{tabular}    \\ \hline
\begin{tabular}[c]{@{}c@{}} General \\ Health \end{tabular} & \begin{tabular}[c]{@{}c@{}} 0  \\ (0\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 11 \\ (100\%) \end{tabular}         \\ \hline
Vaccine        & \begin{tabular}[c]{@{}c@{}} 21     \\ (75\%) \end{tabular}   & \begin{tabular}[c]{@{}c@{}}  7 \\ (25\%)  \end{tabular}     \\ \hline
COVID19     & \begin{tabular}[c]{@{}c@{}} 73 \\ (63\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 43  \\ (37\%) \end{tabular}     \\ \hline
\begin{tabular}[c]{@{}c@{}}  Climate \\ change \end{tabular} & \begin{tabular}[c]{@{}c@{}} 5 \\ (28\%) \end{tabular}  & \begin{tabular}[c]{@{}c@{}} 13 \\ (72\%) \end{tabular}   \\ \hline
\end{tabular}
\caption{}
\label{tab2}
\end{table}

@@

\begin{table*}[h]
\begin{tabular}{|c|c|c|}
\hline
\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Policy \\ regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \begin{tabular}[c]{@{}cl@{}} \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy} \\  \href{https://blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation}{blog.twitter.com/en\_us/topics/company/2021/updates-to-our-work-on-covid-19-vaccine-misinformation} \\  \href{https://blog.twitter.com/en\_us/topics/company/2020/covid-19}{blog.twitter.com/en\_us/topics/company/2020/covid-19}\end{tabular}      \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}cl@{}}  Fighting \\ misinformation \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}cl@{}} \href{https://www.facebook.com/formedia/blog/working-to-stop-misinformation-and-false-news}{facebook.com/formedia/blog/working-to-stop-misinformation-and-false-news}     \\ \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{about.fb.com/news/2018/05/hard-questions-false-news/}   \end{tabular}                            \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   &        \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}{youtube.com/intl/en\_us/howyoutubeworks/our-commitments/fighting-misinformation/\#policies}                                  \\ \hline 
 \end{tabular}
\caption{Summary of ressources, last accessed on July 5, 2021. }
\label{summary}
\end{table*}
